CF Registry Analysis

### 2023-11-30 Christine Chan/CF Registry/cf_registry_analysis.qmd
CF registry survival analysis

```{r}
# Find approximate birth date
annual$approx_birth_year = annual$ReviewYear - ceiling(annual$Age_YrEnd)
annual = annual %>% group_by(eDWID) %>% 
  mutate(approx_birth_year = round(mean(approx_birth_year)))
# Create survival dataset
s <- annual %>%
  rename(end = ReviewYear) %>% # ReviewYear is the end of the interval
  group_by(eDWID) %>%
  mutate(start = lag(end)) %>% # Get interval start
  select(eDWID, start,end, Age_YrEnd, approx_birth_year,cfrd_status_annual) # Sort columns
s$start[is.na(s$start)] = s$approx_birth_year[is.na(s$start)]
# Age group as time-varying covariate
s$age_group <- cut(s$Age_YrEnd,
  breaks = c(-Inf, 10, 19, 31, Inf), right = F,
  labels = c("< 10", "[10,19)", "[19,31)", ">= 31")
)
# Fill down diagnosis
s$cfrd_status_annual[s$cfrd_status_annual=="CFRD-"] = NA
s = s %>% group_by(eDWID) %>% fill(cfrd_status_annual,.direction = "down")
s$cfrd_status_annual[is.na(s$cfrd_status_annual)] = "CFRD-"
# Remove records where start == end
s = s[s$end > s$start,]
# Survival fit
surv_obj = Surv(time = as.numeric(s$start),time2 = as.numeric(s$end),
                event = as.numeric(s$cfrd_status_annual)-1)
fit <- survfit(surv_obj ~ age_group,id = eDWID,data = s)
ggsurvplot(fit,risk.table = T,cumevents = T,
  cumcensor = T,
           fun = "event",xlim = c(2003, 2018))
```

>>>>

```{r}
# Find approximate birth date
annual$approx_birth_year <- annual$ReviewYear - ceiling(annual$Age_YrEnd)
annual <- annual %>%
  group_by(eDWID) %>%
  mutate(approx_birth_year = round(mean(approx_birth_year)))
# Create survival dataset
s <- annual %>%
  rename(end = ReviewYear) %>% # ReviewYear is the end of the interval
  group_by(eDWID) %>%
  mutate(start = lag(end)) %>% # Get interval start
  select(eDWID, start, end, Age_YrEnd, approx_birth_year, cfrd_status_annual) # Sort columns
s$start[is.na(s$start)] <- s$approx_birth_year[is.na(s$start)]
# Age group as time-varying covariate
s$age_group <- cut(s$Age_YrEnd,
  breaks = c(-Inf, 10, 19, 31, Inf), right = F,
  labels = c("< 10", "[10,19)", "[19,31)", ">= 31")
)
# Fill down diagnosis
s$cfrd_status_annual[s$cfrd_status_annual == "CFRD-"] <- NA
s <- s %>%
  group_by(eDWID) %>%
  fill(cfrd_status_annual, .direction = "down")
s$cfrd_status_annual[is.na(s$cfrd_status_annual)] <- "CFRD-"
# Remove records where start == end
s <- s[s$end > s$start, ]
# Survival fit
surv_obj <- Surv(
  time = as.numeric(s$start), time2 = as.numeric(s$end),
  event = as.numeric(s$cfrd_status_annual) - 1
)
fit <- survfit(surv_obj ~ age_group, id = eDWID, data = s)
ggsurvplot(fit,
  risk.table = T, cumevents = T,
  fun = "event", xlim = c(2002, 2018)
)
```
